Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification

### 2019-09-03 190410_Paper_ACPR/paper_v6_r4-1.tex
ACPR_paper: rev 7

Recently, the commercial Wi-Fi device has been adopted for in-air signature authentication due to its easy accessible property \cite{moon2017air}. Based on the distortion of the  Wi-Fi CSI signal according to the user's gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}. 
% omitted
%However, the previous works on Wi-Fi signal based user authentication systems~\cite{hong2016wfid,moon2017air} utilized the conventional feature extraction method such as the Principal Component Analysis. Since the conventional feature extraction method is not enough to extract the direction- or pose-invariant features from the acquired in-air data, 
More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal-based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

@@

\subsection{Triplet network}
% triplet network
The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
\textbf{It is often seen in person re-identification~
\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. Re-identification is an identification problem using the images/videos taken from a different camera~\cite{bedagkar2014survey}. The individual identities are matched based on identity discriminative features. In these problems, the distinction among the classes is challenging since the features are relatively weak compared to the background features. To address this problem, the triplet network optimizes the embedding training data space such that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.}

\textbf{The triplet network receives triplet pairs as its input which is made from a combination of the input data. Since not all triplet samples are contribute to the training ~\cite{schroff2015facenet}, recent issues have highlighted which input pairs will be used for training. To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.}

\textbf{Recently, \cite{schroff2015facenet} adopted additional triplet mining process for the faster convergence speed. They utilized large mini-batch at each training iteration and selected the triplet based on the training network rather than the random sampling. However, this strategy needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs which burden the time.}

%the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data. The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive (similar) data closer to the anchor (reference) data and keeping the negative (dissimilar) data away from the anchor data.
%.... (1. tell how the triplet network solves the problem and not unrelated parts of it. 2. Tell what further issues arise from triplet network?)

% optimize training
%Not clear and no link to above, rewrite this sentence.
%Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary. To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.
%Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed. They utilized large mini-batch at each training iteration and selected the triplet based on the training network.
%However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.

@@

Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh2018learning,toh2018gradient}.
The learning method is grounded on linear algebra with neither learning parameters nor iteration are needed in training.

% Karnet structure and mining samples.
Let the training dataset $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ as the network outputs.
Then the multilayer neural network structure can be written in linear equation form as follows:
\begin{equation}
    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
By adopting the one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$, The trained weight matrices $\mathbf{W}_{i}$ using KAR space manipulation can be obtained as follows~\cite{toh2018gradient}:

\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right).
\end{equation}

@@

% Methods: System overview(Fig.1)
In this section, we propose an identity verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}. Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network.
Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample in the training dataset (see item (a) in Fig.~\ref{fig1}).
Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
The following subsections describe the details of the triplet mining using KAR space learning and the triplet network.

@@

% Methods: KAR learning
\subsection{Triplet mining using kernel and the range space learning}
%1. Need to explain what is "hard" first.
%2. Also, need to explain "anchor sample" before using it.
% description of anchor sample
% loss convergence problem
% we need hard sample selection

\textbf{The triplet network receives triplet data as an input, which consists of the reference data (will be called anchor hereafter) and corresponding positive (same class with the anchor) and negative data (different class with the anchor). The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive data closer to the anchor data and keeping the negative data away from the anchor data.}

According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for faster loss convergence when training the triplet network.
The hard positive sample denotes the positive sample whose distance to the anchor sample is the greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is the smaller (which is most likely to be misclassified as a positive sample). However, there is no information about which sample is hard positive or negative before we train the network.

>>>>

Recently, the commercial Wi-Fi device has been adopted for in-air signature authentication due to its easy accessible property \cite{moon2017air}. Based on the distortion of the  Wi-Fi CSI signal according to the user's gestures, the in-air signature recognition system showed reasonable user verification performance~\cite{moon2017air}.

More recently, some studies attempted to implement the deep learning algorithms in Wi-Fi signal-based user authentication systems to improve the verification performance ~\cite{shi2017smart,pokkunuru2018neuralwave}.

@@

\subsection{Triplet network}
% triplet network
The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
\textbf{It is often seen in person re-identification~\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint} where the individual identities are matched based on discriminative image features. The main difference between person re-identification and identification is the person re-identification is more challenging task by associating images of the same person taken from different cameras or from the same camera in different occasions. }

In these problem, to distinguish among the classes is a challenging task since the features are relatively weak compared to the background features. To address this problem, the triplet network optimizes the embedding data space such that those data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.

The triplet network receives triplet pairs as its input. These triplets pairs are constructed based on a combination of the input data. Since not all triplet samples contribute to the training, recent attention~\cite{schroff2015facenet} has been paid to the choice of relevant input pairs for training. To optimize the training process which utilizes only some parts of the triplet pairs, several researches~\cite{cheng2016person,ding2015deep,wang2016joint} generated triplet \textbf{from a small number of classes (persons) in each iteration.}

Recently, \cite{schroff2015facenet} adopted a triplet mining process to speed up the training convergence. They utilized large mini-batch at each training iteration and selected the triplet based on the training network rather than the random sampling. However, this strategy needed a few thousands of exemplars mini-batch in every training iteration to select the triplet pairs. This results in a heavy computational load in training.

@@

Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh2018learning,toh2018gradient}.
The learning method is grounded on linear algebra with neither learning parameters nor iteration is needed in training.

% Karnet structure and mining samples.
Let $\mathbf{X}\in{\mathbb{R}}^{m \times (n+1)}$ denotes the training data set and $\mathbf{G}\in{\mathbb{R}}^{m \times n}$ denotes the network outputs.
Then the multilayer neural network structure can be written in linear equation form as follows:
\begin{equation}
    \mathbf{G} = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right), i=1,\dotsc,n,
\end{equation}
where $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$,$\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$,$\dots,\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$,$\mathbf{1}=\left[1,\dots,1\right]^{T}\\
\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is activation function.
By adopting the one-hot encoded target $\mathbf{Y}\in{\mathbb{R}}^{m \times n}$ instead of network output $\mathbf{G}$, The trained weight matrices $\mathbf{W}_{i}$ using KAR space manipulation can be obtained as follows~\cite{toh2018gradient}:

\begin{equation}
    \mathbf{W}_{i} = \left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]^{\dagger}\sigma^{-1}\left(\mathbf{Y}\right), i=1,\dotsc,n.
\end{equation}

@@

% Methods: System overview(Fig.1)
In this section, we propose an identity verification system based on the Wi-Fi in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}. Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet input mining together with the triplet network.
Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample in the training dataset (see item (a) in Fig.~\ref{fig1}). \textbf{The hard positive and hard negative samples refer to positive and negative class data which are likely to be misclassified by the network.}
Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
The following subsections describe the details of the triplet mining using KAR space learning and the triplet network.

@@

% Methods: KAR learning
\subsection{Triplet mining using kernel and the range space learning}

The triplet network receives a triplet of data as its inputs. These triplet data set consists of the reference data (will be called anchor samples hereafter) and the corresponding positive class (same class with that of the anchor) and negative class data (different class from that of the anchor). \textbf{The goal of the triplet network is to position the feature vectors in appropriate separation space by putting the positive sample closer to the anchor sample and keeping the negative sample away from the anchor sample.}

\textbf{According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for the faster loss convergence when training the triplet network.
The hard positive sample denotes the positive sample whose distance to the anchor sample is greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is smaller (which is most likely to be misclassified as a positive sample). However, there is no information about which sample is the hard positive or negative before we train the network.}
